### 2020-11-21 pldi21/intro.tex

\subsection{Background}\label{sec:background}
\begin{figure*}
  \includegraphics[width=29pc]{grade-cutoff-livelit.png}
\caption{Grading with Livelits}
\label{fig:grading}
\label{fig:color}
\end{figure*}

% \begin{figure*}
%   \begin{center}
%     \begin{subfigure}[t]{0.5\textwidth}
%       \centering
%        \vspace{-3.4cm}
%        \includegraphics[width=15pc]{graphite-color-palette.png}
%       \vspace{0.1cm}
%       \caption{}
%     \end{subfigure}\begin{subfigure}[t]{0.5\textwidth}
%       \centering
%       \includegraphics[width=15pc]{slider-color-livelits.png}
%       \vspace{-11px}
%       \caption{}
%     \end{subfigure}
%   \end{center}
%   \caption{
%   (a) This figure, adapted from the prior work of \citet{Graphite},
%   shows a Graphite palette associated with the \texttt{Color} class.
%   The client can specify the RGBA components only using literal numbers.
%   (b) A similar Hazel livelit for colors uses live splices for the RGBA components,
%   so the client can enter any Hazel expression.
%   In this case, the client has entered a variable, itself defined using a slider livelit, into the RGB
%   splices. The A splice is filled directly with a slider livelit.
%   The color livelit evaluates splices under its closure to display the
%   computed color.
%   The value of \li{default\_color} is determined by the livelit via a macro expansion step.}
%   \label{fig:color}
% \end{figure*}

>>>>

\subsection{Background}\label{sec:background}

 \begin{figure*}[htb]
   \begin{minipage}[b]{0.3\textwidth}
     \begin{subfigure}[b]{0.3\textwidth}
       \includegraphics[width=15pc]{graphite-color-palette.png}
       \caption{}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
       \includegraphics[width=15pc]{slider-color-livelits.png}
       \caption{}
      \end{subfigure}
  \end{minipage}

  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=15pc]{grade-cutoff-livelit.png}
    \caption{Grading with Livelits}
    \label{fig:grading}
    \label{fig:color}
   \end{subfigure}

 \caption{
   (a) This figure, adapted from the prior work of \citet{Graphite},
   shows a Graphite palette associated with the \texttt{Color} class.
   The client can specify the RGBA components only using literal numbers.
   (b) A similar Hazel livelit for colors uses live splices for the RGBA components,
   so the client can enter any Hazel expression.
   In this case, the client has entered a variable, itself defined using a slider livelit, into the RGB
   splices. The A splice is filled directly with a slider livelit.
   The color livelit evaluates splices under its closure to display the
   computed color.
   The value of \li{default\_color} is determined by the livelit via a macro expansion step.}
   \label{fig:color}
 \end{figure*}
